Foreign direct investment, corporate social responsibility, and malaria control in Mozambique - trends, risks, and opportunities

### 2017-05-22 paper_word.Rmd
big update

---
title: Foreign direct investment, corporate social responsibility, and malaria control in Mozambique - trends, risks, and opportunities
author:
  - name: Joe Brew
    email: joebrew@economicsofmalaria.com
    affiliation: isglobal,cism,vu
    footnote: Corresponding Author
  - name: Elisa Sicuri
    email: elisa.sicuri@isglobal.org 
    affiliation: isglobal,icl,cism
address:
  - code: isglobal
    address: Barcelona Institute for Global Health, c/ Rosselló, 132, 5è 2a. 08036, Barcelona, Spain
  - code: icl
    address: Imperial College London, South Kensington Campus, London SW7 2AZ, U.K.
  - code: cism
    address: Centro de Investigação em Saúde de Manhiça, Vila da Manhiça, Bairro Cambeve, Rua 12, Distrito da Manhiça, CP 1929, Maputo, Mozambique
  - code: vu
    address: VU University Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, Netherlands
abstract: |
  Foreign direct investment (FDI) in Mozambique has increased rapidly in the last two decades. The growing interest in corporate social responsibility (CSR) - combined with a recent push for malaria elimination - suggest the need for a critical examination of the role of FDI in malaria control and elimination. Through a systematic review of the literature, we find that there has been a notable increase in research pertaining to FDI, CSR and malaria in recent years. Consensus among researchers is that this increase has not been accompanied by a substantial private sector investment in malaria control (with a few notable exceptions). This suggests a potential opportunity for scaling up privately driven malaria control as a means to both improve public health and increase return on investment. However, given the lack of coordination between public and private sectors, even when interests coincide, an over-reliance on foreign and private initiative for funding eradication is not without risks.

bibliography: library.bib
output: rticles::elsevier_article
header-includes:
     - \usepackage{longtable}
---

@@

>>>>

---
title: Foreign direct investment, corporate social responsibility, and malaria control in Mozambique - trends, risks, and opportunities
date: "April 5, 2017"
output: word_document
bibliography: library.bib

---

@@

## Abstract

Foreign direct investment (FDI) in Mozambique has increased rapidly in the last two decades. The growing interest in corporate social responsibility (CSR) - combined with a recent push for malaria elimination - suggest the need for a critical examination of the role of FDI in malaria control and elimination. Through a systematic review of the literature, we find that there has been a notable increase in research pertaining to FDI, CSR and malaria in recent years. Consensus among researchers is that this increase has not been accompanied by a substantial private sector investment in malaria control (with a few notable exceptions). This suggests a potential opportunity for scaling up privately driven malaria control as a means to both improve public health and increase return on investment. However, given the lack of coordination between public and private sectors, even when interests coincide, an over-reliance on foreign and private initiative for funding eradication is not without risks.
